Sheafification in HoTT

### 2015-01-13 paper/sheaf_lics.tex

Moreover the following diagram commute
$$\xymatrix{
  \sum_{x:X} (f x = y) \ar[r]^\eta \ar[d]_\gamma & \modal \left(\sum_{x:X}  (f x = y)\right) \ar@{=}[dl]\\
  \sum_{x:\modal X} (\modal f x = \eta_Y y) &
}$$
where $\pi_1 \circ \gamma = \eta_X$, and $\pi_2 \circ \gamma$ is the
usual modalisation of paths.
\end{prop}
\subsection{Generalized pullbacks}
\label{sec:gener-pb}

@@

We define sheaves by induction on the homotopical truncation level of types
~: we define sheaves in $\HProp$ as the classical types ({\em ie}
implied by their double negation), and
we define sheaves on $\Type_{n+1}$ {\em via} usual definition of sheaves,
as seen in~\cite{maclanemoerdijk} and sheaves on $\Type_n$. Of course,
the definition must be cumulative.

@@

@@

@@

We now need to show that $\square$ is universal. The following
lemma is central in the proof~:
\begin{lem}
  Let $T:\Type_{n+1}$. Then $\square T$ is the colimit of the closed
  diagonal diagram
  $$\xymatrix{ 
    \cdots \overline{\Delta_3} \tar[r] & \overline{\Delta_2} \dar[r] &
    \overline{\Delta_1}
  }$$
where $\Delta_k$ is the $k$-pullback of $\id : T \to T$.
\end{lem}
\begin{proof}
  As $\mu_T$ is an embedding, we know by Giraud axiom that $\square T$ is the colimit
  of $C(\mu_T)$. If we can show that $C(\mu_T) = C(\id)$, the the
  result will follow.

>>>>

Moreover the following diagram commute
$$\xymatrix{
  \sum_{x:X} (f x = y) \ar[r]^\eta \ar[d]_\gamma & \modal \left(\sum_{x:X}  (f x = y)\right) \ar@{=}[dl]\\
  \sum_{x:\modal X} (\modal f x = \eta_Y y) &
}$$
where $\pi_1 \circ \gamma = \eta_X$, and $\pi_2 \circ \gamma$ is the
usual modalisation of paths.
\end{prop}

Another useful properties of modalities is the following~:
\begin{prop}
  If $P:\HProp$, then $\modal \widehat P : \HProp$, where $\widehat P$
  is $P$ seen as a $p$-type.
\end{prop}

A left exact modality leads to a new theory with new principles. A
basic example is the {\em open modality of $P$} for a $P:\HProp$, $\modal_P T = P \to T$. 
When one works in the subuniverse defined by this modality, defining
an inhabitant of a type $T$ is actually an inhabitant of $P \to
T$. Thus, being in this subuniverse is just adding the axiom $P$ to
the theory. Sadly, adding an axiom using the modality does not add any
computational content to $P$, thus it is not completely satisfactory.

Another example is the $\lnot\lnot$-modality, $\modal_{\lnot\lnot} T = (T
\to \bot) \to \bot$. Although we might think it enables us to use
classical reasonings in the corresponding reflective subuniverse, the
main problem is that every type in the new universe is an $\HProp$,
which is very restrictive.

\subsection{Generalized pullbacks}
\label{sec:gener-pb}

@@

We will define sheaves by induction on the homotopical truncation level of types
~: the base case will be any left exact modality on $\HProp$, and we
give in this section some definitions useful for th inductive case.

@@

Note that these definitions are almost the same as the ones
in~\cite{maclanemoerdijk}. The main difference is that {\em separated}
is defined for $n$-subobjects,
while {\em sheaf} only for $-1$-subobject.

@@

There again, the separation step has the same definition as
in~\cite{maclanemoerdijk}, using $\Type_n^\modal$ instead of the
$j$-subobject classifier.

@@

We now need to show that $\square$ is universal. The following
lemma is central in the proof~:
\begin{lem}
  Let $T:\Type_{n+1}$. Then $\square T$ is the colimit of the closed
  diagonal diagram
  $$\xymatrix{ 
    \cdots \overline{\Delta_3} \tar[r] & \overline{\Delta_2} \dar[r] &
    \overline{\Delta_1}
  }$$
where $\Delta_k$ is the $k$-pullback of $\id : T \to T$.
\end{lem}

This lemma is an adaptation of the sheafification process
in~\cite{maclanemoerdijk}, where they consider only the kernel pair of
$\mu_T$ instead of the \v{C}ech nerve.

\begin{proof}
  As $\mu_T$ is an embedding, we know by Giraud axiom that $\square T$ is the colimit
  of $C(\mu_T)$. If we can show that $C(\mu_T) = C(\id)$, the the
  result will follow.
